---
title: "RWorksheet_Benedicto#4a.R"
author: "Miguel F. Josue Jr"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
data <- data.frame(
  Shoe_Size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5,12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M","M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)
data


```
a. Describe the data.
The table provides a summary of data  about individuals' shoe size, height, and gender. Whereas shoe size and height are in a numeric data types since they are measurements while the gender(F and M) correspond to the initial characters of male and female. The table implies that there is a correlation between these variables.

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
- The R scripts displays the gender-based shoe size and height data, through the "select" function we are able to only view only the Shoe Size and Height, this is used in order to avoid redundancy.
```{r}
male_data <- subset(data, Gender == "M",select = c(Shoe_Size, Height))

male_data
```
```{r}
female_data <- subset(data, Gender == "F", select = c(Shoe_Size, Height))

female_data
```
c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
mean_shoe_size <- mean(data$Shoe_Size)
mean_shoe_size
mean_height <- mean(data$Height)
mean_height
```
d. Is there a relationship between shoe size and height? Why?
- There is indeed a relationship between shoe size and height, as the height increases the shoe size also increase relatively. It is also observed in the data that men have a significant gap in both said variables compared to women.

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r}
months_vector <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February",
"April")

factor_months_vector <- factor(months_vector)

print(factor_months_vector)

levels(factor_months_vector)
```
3. Then check the summary() of the months_vector and factor_months_vector. Inter-
pret the results of both vectors. Are they both equally useful in this case?
  The summary(month_vector) presents the length and other generic properties of the vector like Class and mode, while the summary(factor_months_vector) counts the occurrences of each month .
 Both these summaries provide significant data, one shows the structure of the vector while the other is more on classifying categorical data.
```{r}
summary(months_vector)
```
```{r}
summary(factor_months_vector)
```
4. Create a vector and factor for the table below.
```{r}
direction_vector <- rep(c("East", "West", "North"),c(1,4,3))

factor_data <- factor(direction_vector)

new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```
5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
b. View the dataset. Write the R scripts and its result.
```{r}
file <- read.table("import_march.csv", header = TRUE, sep = ",")
print(file)
```