---
title: "RWorksheet_Josue#1.Rmd"
author: "Miguel F. Josue Jr"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

  
 
1.Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41.
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)
length(age)
```
- There are 34 data points

2.Find the reciprocal of the values for age.
```{r}
reciprocal <- 1/age
reciprocal
```
3.Assign also new_age <- c(age, 0, age).
```{r}
new_age <- c(age, 0, age)
new_age
length(new_age)
```
- After running the said code chunk the new_age object iterated what is defined in the parentheses specifically the vector in age, a O , and another iteraton of age which resulted to 69 data points overall.

4.Sort the values for age.
```{r}
sort(age)
```
5.Find the minimum and maximum value for age.
```{r}
min(age)
max(age)
```
6.Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, and 2.7.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
length(data)
```
 - There are 12 data points

7.Generates a new vector for data where you double every value of the data. | What
happen to the data?
```{r}
new_data <- data*2
new_data
```
- All elements of the data object was doubled

8.Generate a sequence for the following scenario:

8.1
```{r}
hundred <-seq(1,100)
hundred
```
8.2
```{r}
even<-seq(20,60)
even
```
8.3
```{r}
mean <- mean(even)
mean
```
8.4
```{r}
sum <-sum(51:91)
sum
```
8.5.
```{r}
thousand <- seq(1,1000)
thousand
len_hun <- length(hundred)
len_eve <- length(even)
len_mean <- length(mean)
len_sum <- length(sum)
total_length <- len_hun + len_eve + len_mean + len_sum
total_length
seq_1_to_1000 <- 1:1000
max_to_10 <- max(seq_1_to_1000[seq_1_to_1000 <- 10])
max_to_10
```
- There are 143 data points from 8.1 to 8.4
9. *Print a vector with the integers between 1 and 100 that are not divisible by 3, 5 and
7 using filter option.
```{r}
Filter(function(i) { all(i %% c(3,5,7) != 0) }, seq(100))

```
10. Generate a sequence backwards of the integers from 1 to 100.
```{r}
ten <- seq(100,1)
ten

```
11.List all the natural numbers below 25 that are multiples of 3 or 5.
```{r}
numbers <- 1:24
len_num <- length(numbers)
multiples <- numbers[numbers %% 3 == 0 | numbers %% 5 == 0]
sum_multiples <- sum(multiples)
tenleven_len <- length(ten)+length(numbers) + length(multiples)+ length(sum_multiples)
tenleven_len
```
- There are 136 data points

12. Statements can be grouped together using braces ‘{’ and ‘}’. A group of statements
is sometimes called a block. Single statements are evaluated when a new line is typed
at the end of the syntactically complete statement. Blocks are not evaluated until a
new line is entered after the closing brace.
Describe the output.
```{r}
# x <- {0 + x + 5 + }

```
- The output results to an error due to missing values, the console also states this error message (Error: unexpected '}' in "x <- {0 + x + 5 + }")

13. *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75,
75 and 77. To access individual elements of an atomic vector, one generally uses the
x[i] construction.
Find x[2] and x[3]. Write the R code and its output.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
element_2 <- score[2]
element_3 <- score[3]

element_2
element_3
```
14. *Create a vector a = c(1,2,NA,4,NA,6,7).
```{r}
a <- c(1,2,NA,4,NA,6,7)
print(a,na.print="-999")
```
- The NA value in the vector is changed to -99 as per order of the print function. The statements in the parentheses are specificities . 

15.A special type of function calls can appear on the left hand side of the assignment
operator as in > class(x) <- "foo".

```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```
- This type of codes are similar to the functions scanf and input statements, this allow users to store data within an object. A very standard input process...










 












    