---
title: "RWorksheet_Josue#3b"
author: "Miguel F. Josue Jr."
date: "2024-10-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Create a data frame using the table below.

```{r}
#a. Write the codes.
data <- data.frame(
  Respondents = 1:20,
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 1, 1, 2, 1, 2, 3, 2, 3, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_School = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
data

#b.Describe the data. Get the structure or the summary of the data
  #The dataset consists of 20 respondents, with information on their sex, father's occupation, household size, number of siblings attending school, and type of house.
str(data)
summary(data)

#c. Is the mean number of siblings attending is 5?
mean1 <- mean(data$Siblings_at_School)
print(paste("No, since the mean is", mean1))

#d. Extract the 1st two rows and then all the columns using the subsetting functions.Write the codes and its output.
subset_data <- subset(data, Respondents <= 2)
subset_data

#e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.s
oddr_evenc <- data[c(3, 5), c(2, 4)]
oddr_evenc

#f. Select the variable types of houses then store the vector that results as types_houses.Write the codes.
types_houses <- data$Types_of_Houses
types_houses

#g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.
male_farmers <- subset(data, Sex == 1 & Fathers_Occupation == 1)
male_farmers
#no data found(!)

#h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.
# Select female respondents with 5 or more siblings attending school
female_siblings <- subset(data, Sex == 2 & Siblings_at_School >= 5)
female_siblings
```
2. Write a R program to create an empty data frame. Using the following codes:
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))

#a. Describe the results.
    # The code outputs the structure of an empty data frame with 0 observations (rows) and 5 variables (columns).
```
3. Create a .csv file of this. Save it as HouseholdData.csv

```{r}
#a. Import the csv file into the R environment. Write the codes.
houseHoldData <- read.csv("HouseholdData.csv")
houseHoldData

#b. Convert the Sex into factor using factor() function and change it into integer.[Legend:Male = 1 and Female = 2]. Write the R codes and its output.
houseHoldData$Sex <- factor(houseHoldData$Sex, levels = c("Male", "Female"), labels = c(1, 2))
houseHoldData$Sex <- as.integer(houseHoldData$Sex)
houseHoldData

#c. Convert the Type of Houses into factor and change it into integer. [Legend: Wood = 1; Congrete = 2; Semi-Congrete = 3]. Write the R codes and its output.
houseHoldData$Types.of.Houses <- factor(houseHoldData$Types.of.Houses, levels = c("Wood", "Congrete", "Semi-congrete"), labels = c(1, 2,3))
houseHoldData$Types.of.Houses <- as.integer(houseHoldData$Types.of.Houses)
houseHoldData

#d. On father’s occupation, factor it as Farmer = 1; Driver = 2; and Others = 3. What is the R code and its output?
houseHoldData$Fathers.Occupation <- factor(houseHoldData$Fathers.Occupation, levels = c(1, 2,3), labels = c("Farmer", "Driver", "Others"))
houseHoldData

#e. Select only all females respondent that has a father whose occupation is driver. Write the codes and its output.
femdrivers  <- houseHoldData[houseHoldData$Sex == 2 & houseHoldData$Fathers.Occupation == "Driver", ]
femdrivers

#f. Select the respondents that have greater than or equal to 5 number of siblings attending school. Write the codes and its output.
morefive <- houseHoldData[houseHoldData$Siblings.at.School >=5,]
morefive
```
4.Interpret the graph.

  The graph titled "Sentiments of Tweets Per Day" provides a breakdown of tweet sentiments (Negative, Neutral, and Positive) across six days, from July 14 to July 21, 2020. The data indicates that Negative sentiment consistently dominates, with significant peaks on July 15 and July 21, each exceeding 4,000 tweets. Neutral sentiment remains fairly stable, though it fluctuates between 2,500 to 3,500 tweets, showing less dramatic changes. Positive sentiment is the least prevalent but experiences a noticeable rise on July 17 and July 18. The overall pattern suggests that during this period, public sentiment was largely negative, with fewer neutral or positive responses. The spikes in negative tweets may reflect reactions to specific events occurring on those particular days.







