---
title: "RWorksheet_Benedicto#4a.R"
author: "Miguel F. Josue Jr"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
data <- data.frame(
  Shoe_Size = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5,12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0),
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M","M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)
data


```
a. Describe the data.
The table provides a summary of data  about individuals' shoe size, height, and gender. Whereas shoe size and height are in a numeric data types since they are measurements while the gender(F and M) correspond to the initial characters of male and female. The table implies that there is a correlation between these variables.

b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
- The R scripts displays the gender-based shoe size and height data, through the "select" function we are able to only view only the Shoe Size and Height, this is used in order to avoid redundancy.
```{r}
male_data <- subset(data, Gender == "M",select = c(Shoe_Size, Height))

male_data
```
```{r}
female_data <- subset(data, Gender == "F", select = c(Shoe_Size, Height))

female_data
```
c. Find the mean of shoe size and height of the respondents. Write the R scripts and its
result.
```{r}
mean_shoe_size <- mean(data$Shoe_Size)
mean_shoe_size
mean_height <- mean(data$Height)
mean_height
```
d. Is there a relationship between shoe size and height? Why?
- There is indeed a relationship between shoe size and height, as the height increases the shoe size also increase relatively. It is also observed in the data that men have a significant gap in both said variables compared to women.

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r}
months_vector <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February",
"April")

factor_months_vector <- factor(months_vector)

print(factor_months_vector)

levels(factor_months_vector)
```
3. Then check the summary() of the months_vector and factor_months_vector. Inter-
pret the results of both vectors. Are they both equally useful in this case?
  The summary(month_vector) presents the length and other generic properties of the vector like Class and mode, while the summary(factor_months_vector) counts the occurrences of each month .
 Both these summaries provide significant data, one shows the structure of the vector while the other is more on classifying categorical data.
```{r}
summary(months_vector)
```
```{r}
summary(factor_months_vector)
```
4. Create a vector and factor for the table below.
```{r}
direction_vector <- rep(c("East", "West", "North"),c(1,4,3))

factor_data <- factor(direction_vector)

new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
```
5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
b. View the dataset. Write the R scripts and its result.
```{r}
file <- read.table("import_march.csv", header = TRUE, sep = ",")
print(file)
```
6. Create an R Program that allows the User to randomly select numbers from 1 to 50. Then display the chosen number. If the number is beyond the range of the selected choice, it will have to display a string "The number selected is beyond the range of 1 to 50". If number 20 is inputted by the User, it will have to display "TRUE", otherwise display the input number.
```{r}
#Full Search
exhaustive_search <- function(input_number) {
  if (is.na(input_number)||input_number < 1 || input_number > 50) {
    return("The number selected is beyond the range of 1 to 50")
  } else if (input_number == 20) {
    return("TRUE")
  } else {
    return(paste("The selected number is:", input_number))
  }
}

input_number <- as.integer(readline(prompt = "Enter a number between 1 and 50: "))
result <- exhaustive_search(input_number)
print(result)
```
7. At ISATU University's traditional cafeteria, snacks can only be purchased with bills. A long-standing rule at the concession stand is that snacks must be purchased with as few coins as possible. There are three types of bills: 50 pesos, 100 pesos, 200 pesos, 500 pesos, 1000 pesos.
a. Write a function that prints the minimum number of bills that must be paid, given the price of the snack.

```{r}
#Change
min_bills <- function(price) {
  available_bills <- c(1000, 500, 200, 100, 50)
  total_bills <- 0
  
  for (bill in available_bills) {
    if (is.na(price) || is.na(bill)||price >= bill) {
      count <- floor(price / bill)
      price <- price - count * bill
      total_bills <- total_bills + count
    }
  }
  
  return(total_bills)
}

price <- as.numeric(readline(prompt = "Enter the price of the snack: "))
print(paste("Minimum number of bills needed to purchase a snack:", min_bills(price)))

```
8. The following is each student's math score for one semester. Based on this, answer the following questions.
A. Create a dataframe from the above table. Write the R codes and its output.
```{r}
grades <- data.frame(
  Name = c("Annie", "Thea", "Steve", "Hanna"),
  Grade1 = c(85, 65, 75, 95),
  Grade2 = c(65, 75, 55, 75),
  Grade3 = c(85, 90, 80, 100),
  Grade4 = c(100, 90, 85, 90)
)

grades
```
B. Without using the rowMean function, output the average score of students whose average math score over 90 points during the semester. write R code and its output.
```{r}
for (i in 1:nrow(grades)) {
  total_score <- sum(grades[i, 2:5])  
  avg_score <- total_score / 4  
  if (avg_score > 90) {
    print(paste(grades$Name[i], "'s average grade this semester is", avg_score))
  }
}
#NO average score OVER 90 (highest is flat 90)
```
C. Without using the mean function, output as follows for the tests in which the average score was less than 80 out of 4 tests.
```{r}
for (j in 2:5) {
  total_score <- sum(grades[, j])  
  avg_score <- total_score / nrow(grades)  
  if (avg_score < 80) {
    test_num <- j - 1  
    print(paste("The Grade",test_num, "test was difficult."))
  }
}
```
D.Without using the max function, output as follows for students whose highest score for a semester exceeds 90 points.
```{r}
for (i in 1:nrow(grades)) {
  highest_score <- grades[i, 2]  
  for (j in 3:5) {  
    if (grades[i, j] > highest_score) {
      highest_score <- grades[i, j]
    }
  }
  if (highest_score > 90) {
    print(paste(grades$Name[i], "'s highest grade this semester is", highest_score))
  }
}
```





